Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Proposing a paragraph to connect with ongoing work about measurement in scientific software communities, including a working paper and website that outlines appropriate measures and practices. Perhaps too post-workshop but I hate to see things unconnected.  Certianly the cite to the Millington book is appropriate, given that it came up in the discussion (well, I brought it up) and was in the notes

\subsubsection{Challenges of community}
include metrics for community success (e.g., more external
contributors than internal).

>>>>

\subsubsection{Measuring community}
How might a project know when it has built a sustainable community?  How might an outsider be able to assess the activity and sustainability of that community?  These questions have been partially addressed in the literature.  For example, a key metric in online communities in general is the cross-over point where there are more external contributors than internal ones. Richard Millington's book ``Buzzing Communities'' does an excellent job of outlining these measures, drawing on online communities research in an accessible manner~\cite{millington_buzzing_2012}. Some participants in the workshop have since prepared online materials outlining current and future practices in measurement of scientific software and its ecosystem\footnote{\url{https://sites.google.com/site/scientificsoftwaremetrics/}}.
